\chapter{123HelpMe.com - The Development of Pip in \textit{Great Expectations} \cite{essaydickens}}

As Pip grows throughout the novel, he develops and matures from a naive, young boy to a moral gentleman by the three main stages that take place 
throughout his life. \\

In the first stage of Pip's life he is young and does not understand what it means to be a gentleman and how it can affect his life. Pip basically 
asks for three wishes in the first stage. He wants education, wealth, and social advancement. These three wishes are mostly so he can impress 
Estella, who is the symbol of this first stage. Pip does not want to be a lowly blacksmith like Joe. He wants to be intelligent. He wants to be 
considered a person of high importance. At the end of this stage he moves to London and begins to see the problems in the fog ahead. \\

In the second stage Pip is able to live his dreams of being educated and wealthy. As the second stage progresses he has less and less time for other 
people outside of his little circle. He mistreats Joe and Biddy.  He finds he is embarrassed to be around them. His relationship with Estella also 
worsens.  They had not seen each other in years and the small bond that they had broke in time. Estella then marries Drummle instead of Pip and all 
his hopes for her are lost as well. Pip also begins to spend too much money and goes into debt even with his secret benefactor giving him money. 
Once Pip discovers who his benefactor truly is all his dreams are shattered. He cannot believe a criminal had been supplying him with money all this 
time.  Stage two ends with Pip being broken and destroyed with all the problems he faces. \\

In the third stage Pip tries to repair all his relationships with people he mistreated and loved. Pip finds Herbert a good job even if it means Pip 
using some of his own money.  Pip also tries to help Magwitch escape.  Although Magwitch does not escape, Pip makes Magwitch happy before he dies 
telling him that he has a daughter and that he is in love with her.  Pip also helps Miss Havisham discover the error of her ways.  She is happy Pip 
has shown her this and would like to give Pip some money to help him with his debts.  Pip does not take the offer and knows that he himself must work 
hard to pay off his debts.  Pip then goes to his home in the marshes.  Joe pays off all his debts and their relationship is now repaired. Pip also 
meets Little Pip, the symbol of rebirth.  Pip fixed all his problems and was never again faced with them because he decided to live with the people 
he loved, Joe and Biddy, his family. \\

At the end Pip matured from a boy who did not truly understand the burdens of being wealthy to a young gentleman who was deeply in debt and only had 
his one friend Herbert by his side, to a young man living in the marshes with his family with no problems whatsoever.

\chapter{Eiffel 65 - Too Much Of Heaven \cite{chansoneiffel}}

\emph{Song lyrics transcription from album \textbf{Europop}} \\
\begin{small}
Copyright \copyright\ 1999 Universal Music
\end{small}
\\ \\
Too much of heaven, \\
Can bring you underground \\
Heaven, can always turn around. \\
Too much of heaven, \\
A life and soul hell bound. \\
Heaven, the killer makes no sound. \\
\\
They're still talking about money, \\
That's right and too much of heaven. \\
C'mon my friend. \\
\\
Let me tell you what it's all about, \\
It's called money dependence today, \\
And people just keep on going on \\
Looking at the dollar bill, \\
And nothing else around them. \\
No love, no friendship, nothing else, \\
Just the dollar bill coming on into their pocket, \\
Into their bank account, \\
And that's too much of heaven \\
Bringing them underground. \\
Let me tell you what it's all about \\
It's called money dependence today, \\
And people just keep on going on \\
Looking at the dollar bill, \\
And nothing else around them. \\
No love, no friendship, nothing else, \\
Just the dollar bill coming on into their pocket, \\
Into their bank account, \\
\\
The answer, \\
Is blowing in the wind. \\
The answer is blowing. \\
\\
Oh let me tell you what it's all about. \\
Too much of heaven bring you underground.

\chapter{Yann Fi\'{e}vet - La cupidit\'{e} \cite{articlefievet}}

\section{Summary}

Le capitalisme puise son énergie dans la cupidité de l'Homme, moteur d'une machine incontrôlable et aux multiples facettes, 
semant avec rage les produits de la mondialisation. Ce sentiment, initié à l'esprit de nos consciences, hier presque vierge 
de toutes valeurs immorales,  a permis d'étendre et de renforcer notre besoin d'accumulation matérielle à moindre coût. En 
effet, la course à la petite économie ne fait qu'entretenir un monde virtuel et illusoire dans lequel l'Homme se passionne 
pour le neuf et l'élégance subtile de concepts anciens remis au goût du jour. Alors que la Chine et l'Inde contribuent 
férocement à la satisfaction récurrente d'une société de consommation en péril, les autres géants de ce monde se contentent 
d'appliquer sans cesse les lois de la délocalisation, se procurant avec simplicité de la matière grise performante et peu 
coûteuse. L'\oe uf asiatique ne fait qu'éclore, sa puissance créatrice et sa cupidité exacerbée rendant envieux des patrons 
européens qui ne font qu'observer le reste du monde trembler.

\section{Excerpt}

Nous sommes cupides, ils le seront davantage encore.\\

Le capitalisme a de très beaux jours devant lui. Son ressort principal réside dans l'avidité sans fin des hommes. 
Avidité pour l'argent et les objets innombrables qu'il permet d'acquérir. On stigmatise souvent les Américains sous 
ce point de vue. Les Européens sont-ils si différents. Ils seront départagés, c'est certain, dans un avenir proche 
par les Chinois qui, dans leur <<atelier du Monde>> concocteront les ingrédients du capitalisme irrépressible et 
dénué du moindre artifice. Contrairement à une idée reçue, académiquement ressassée, le capitalisme n'est plus capable, 
depuis une trentaine d'années, de créer des richesses nouvelles susceptibles d'améliorer le sort des hommes les plus 
démunis dont le nombre ne cesse de croître. C'est pour cette raison indépassable qu'il est dès lors condamné à valoriser 
des richesses existantes jusque-là tenues à distance de l'accaparement par le Marché. Tout doit devenir marchandise, 
l'\'{E}cole, la Santé, les biens communs telle l'eau, les gènes et les corps, l'identité même des personnes, afin que 
continue d'être alimenté le moteur d'une machine ne tournant plus que sur elle-même. Elle tourne sur elle-même mais 
rejette en dehors d'elle tout ce qu'elle ne sait ou ne peut digérer : montagnes d'objets obsolètes dont quelques-uns 
sont sauvés du naufrage en vue de garnir un jour les vitrines des musées, nuées de pollutions mortifères et nauséabondes. 
Partout, la machine crée, par les effets prodigieux de son propre fonctionnement, le désordre potentiel que les hommes 
ne font jamais que contenir ici pour mieux le laisser embellir ailleurs. Quand la machine sera parfaitement mondialisée, 
sa puissance sera parfaitement incontrôlable. Cette valorisation, au sens mercantile du terme, affaiblit, à mesure qu'elle 
étend sa toile, les valeurs morales que seule une vigilance scrupuleuse permet de renforcer tant leur présence au sein des 
communautés humaines n'a rien de naturel. Dans l'hypermarché planétaire ouvert au vent de la fièvre consumériste, une valeur 
prime toutes les autres : l'accumulation matérielle. Nous y cédons tous, tous nous sommes à l'affût de <<la bonne affaire>>.
Certains en usent avec parcimonie ; d'autres en abusent jusqu'au ridicule. Les pauvres n'y échappent pas. Seuls les miséreux 
en sont exclus. Les tours-opérateurs vendent du voyage au kilomètre et à bas prix à des gogos incapables de rêver sur place. 
Ils n'en reviennent pas tous. Le culte de l'illusion a besoin de rites sacrificiels. Les aventuriers de pacotille doivent 
apprendre à mesurer le prix de la liberté artificielle qu'ils croient avoir méritée. \\

En un mot, nous sommes cupides. Une cupidité inlassablement alimentée par l'étonnement que savent susciter les marchands et 
autres publicitaires. Nous sommes dans un émerveillement perpétuel pour le neuf. Nous aimons le nouveau et on nous en abreuve 
jusqu'à plus soif. Peu importe que la plupart du temps le neuf ne soit que de l'ancien habilement rafraîchi. <<La surprise 
des nouvelles nourritures excitait la cupidité des estomacs>>, écrivait Flaubert. Hélas! les esprits aussi sont atteints 
par le funeste penchant. Pour satisfaire l'envie permanente de surprise il faut un flot croissant d'objets au prix décroissant 
fabriqués par une main d'oeuvre abondante et peu coûteuse. Est-ce le fruit du hasard si le pays le plus peuplé de la planète 
s'apprête à devenir l'atelier du Monde et à inonder inexorablement celui-ci de sa production réalisée au mépris total de l'Homme 
et de son environnement naturel. La bonne vieille théorie de Ricardo sur la spécialisation des nations prend une réalité 
démentielle. Si les Chinois deviennent les ouvriers du Monde, les Indiens vont devenir les producteurs de services <<haut de 
gamme>> pour la planète entière. Ils se forment très vite et très bien. Les multinationales américaines délocalisent leurs 
activités en Inde où elles trouvent des ingénieurs de pointe défiant toute concurrence. Une autre théorie, celle de la force 
d'inertie des masses, ne peut que nous effrayer. La population cumulée de la Chine et de l'Inde représente 40\% de l'humanité. 
On ne pourra rien contre cette puissance démographique. Cela commence par une pression énorme sur les conditions de travail, les 
salaires et la protection sociale en Occident. Comment cela finira-t-il? Dans ce contexte de concurrence internationale exacerbée, 
les patrons de firmes européennes sont aux abois. Il faut leur faciliter la tâche, leur permettre enfin de s'aligner sur les 
pratiques qui font le succès des concurrents asiatiques. En France, un homme a enfin compris cela. M. Raffarin sait que notre 
cupidité est trop timorée, une cupidité d'enfants de choeur pour dire vrai. Il était plus que temps d'envier celle des Chinois. 
Quand le grand Hugo écrivait <<Quand la Chine s'éveillera, le monde tremblera>>, il ne se trompait que d'un verbe. Craignons 
que ce monde ne périsse à tout jamais!

\chapter{Robert Schenk - What is Money? \cite{articleschenk}}

\section{Summary}

Robert Schenk, who is teaching undergraduate economics since 1970 and has published articles in various economic journals, is explaining in this 
article the main purposes which money was invented for, specifically the need to establish a standard of value that would permit to make trading 
easier. In spite of different meanings given to money in current uses of that word such as income, wealth or profit, he defines money as a medium 
of exchange. Moreover, he says that money is also useful because it reduces the cost of transactions in complex trading patterns. He also deals 
with money as a store of value, that means it is a way to hold wealth, but it is not the only one, alternatives are for example real estate and 
valuable art objects. In order to clarify the need to establish such a standard of value, the author decribes an example of a basic barter 
economy. Extending that example to a more complex barter situation makes the reader realize that without money, buying things would be very 
difficult, and impossible in certain cases. To sum up, the author states three aspects of the establishment of money : a medium of exchange, a 
standard of value and a store of value.

\section{Excerpt}

Economists often use words in ways that are not quite the same as the way the words are used in everyday speech. <<Money>> is such a word. In 
everyday speech we use the word <<money>> in a variety of ways, such as: <<My father makes a lot of money>>, or <<John Paul Getty had more money than 
anyone else>>, or <<General Motors made twice as much money this year as last>>. In the first sentence above the word money could be replaced with 
income, in the second with wealth, and in the third with profit or net income. None is the way economists usually use the word <<money>>. The 
economic definition emphasizes that money is the medium of exchange, or what we use to buy things with. \\

Economic activity can take place without money. All transactions can be barter transactions in which people obtain a good or service that they 
want by trading away some other good or service that they value less. Because barter is inconvenient, barter systems exist only when exchange is 
uncommon. Suppose Crusoe has fish and Friday has coconuts. If Crusoe visits Friday to buy coconuts, a trade may not take place. Crusoe wants 
coconuts, but Friday does not want fish. Exchange will take place only when one of the three realizes that he will have to accept something he 
does not want but which he can trade later. With only three people and three commodities, this realization will soon take place. However, if 
there are a hundred people with a hundred different commodities, the pattern of barter transactions necessary for everyone to end up with what he 
or she wants may be so complex that trade may not occur.1 As trading patterns become more complex, groups need to find a way to reduce the cost 
of making transactions. They spontaneously begin to use one commodity as an intermediary: they invent money. \\

The invention of money makes trading easier. With money, all prices can be expressed in the same way, in terms of how much money is needed to 
buy the product. The unit of money becomes the measuring stick of value, or what economists call the standard of value. With a standard of value, 
computing the costs and benefits of various options, that is, making choices, becomes easier.
 
A standard of value is most useful when it does not change over time. If the measuring stick changes with time, comparing costs and benefits of 
some options may be more difficult. Inflation or deflation change the measuring stick, and a reason people dislike inflation is that it makes 
comparing options over time more difficult.

In addition to its function as a medium of exchange, money also serves as a store of value. Though this function is not what makes money important 
in macroeconomics, it is vital in explaining how much money people want to hold. Any item that people consider as a way of holding wealth is a 
store of value. Land, stocks and bonds, old paintings, factories, and jewelry are just some of the other ways people can hold wealth. When money 
is a good way to hold wealth compared to these alternatives, people will want to hold a lot of it. On the other hand, when money is a poor way to 
hold wealth, people try to keep little of it. For example, in the German hyperinflation people tried to spend money as soon as they got it because 
it lost value so quickly. This idea, that people are willing to hold large amounts of money when it is a good store of value, but try to hold small 
amounts when it is a poor way to hold wealth, is a key idea for those who believe that changes in the amount of money have been an important source 
of economic disturbance.

\chapter{Money for sex By D. Brian Burghart}

Let's talk about an aspect of the cover story that we don't discuss directly. I don't know whether I believe prostitution should be legal. I was a bartender for 13 years, and I've known many prostitutes. In those years, I dated two ex-prostitutes.

Those relationships make me feel that I am at least qualified to discuss the question. I mean, when you date somebody who was a prostitute, you spend some time thinking about all those men, all those acts. As a couple, you certainly spend some time discussing such things.

At any rate, there are two sides to the argument: Prostitution should be legal because it empowers women, who should be able to decide what they do with their bodies. Prostitution should be illegal because it exploits women. Forgive my sexism; I've known a guy or two who's turned a trick or two, but I think the bigger issue is licensed prostitutes in Nevada.

I can say without hesitation that I've never known a prostitute, legal or illegal, who was emotionally well-adjusted. I've known some who were more normal than others, but I've never known one who became a prostitute as a career choice. Even the top-dollar call girl got into the business out of desperation. The problem in my morally relativistic world is that those women, by taking that road, may have been saved from something worse, like abusive, murderous husbands.

I guess that's the quandary in a nutshell. The prostitutes I have known were both exploited and empowered. In this world where the power structure spends more time moralizing than giving people tools to avoid those most desperate acts of survival, I'm not going to suggest the final shred of net be removed because I don't really know what happens to people who hit bottom and keep going. Seems like there should be a higher safety net, though. 


\chapter{CEOs say how you treat a waiter can predict a lot about character By Del Jones, USA TODAY}

Office Depot CEO Steve Odland remembers like it was yesterday working in an upscale French restaurant in Denver.

The purple sorbet in cut glass he was serving tumbled onto the expensive white gown of an obviously rich and important woman. "I watched in slow motion ruining her dress for the evening," Odland says. "I thought I would be shot on sight."

Thirty years have passed, but Odland can't get the stain out of his mind, nor the woman's kind reaction. She was startled, regained composure and, in a reassuring voice, told the teenage Odland, "It's OK. It wasn't your fault." When she left the restaurant, she also left the future Fortune 500 CEO with a life lesson: You can tell a lot about a person by the way he or she treats the waiter.

Odland isn't the only CEO to have made this discovery. Rather, it seems to be one of those rare laws of the land that every CEO learns on the way up. It's hard to get a dozen CEOs to agree about anything, but all interviewed agree with the Waiter Rule.

They acknowledge that CEOs live in a Lake Wobegon world where every dinner or lunch partner is above average in their deference. How others treat the CEO says nothing, they say. But how others treat the waiter is like a magical window into the soul.

And beware of anyone who pulls out the power card to say something like, "I could buy this place and fire you," or "I know the owner and I could have you fired." Those who say such things have revealed more about their character than about their wealth and power.

Whoever came up with the waiter observation "is bang spot on," says BMW North America President Tom Purves, a native of Scotland, a citizen of the United Kingdom and Northern Ireland, who lives in New York City with his Norwegian wife, Hilde, and works for a German company. That makes him qualified to speak on different cultures, and he says the waiter theory is true everywhere.

The CEO who came up with it, or at least first wrote it down, is Raytheon CEO Bill Swanson. He wrote a booklet of 33 short leadership observations called Swanson's Unwritten Rules of Management. Raytheon has given away 250,000 of the books.

Among those 33 rules is only one that Swanson says never fails: "A person who is nice to you but rude to the waiter, or to others, is not a nice person."

Swanson says he first noticed this in the 1970s when he was eating with a man who became "absolutely obnoxious" to a waiter because the restaurant did not stock a particular wine.

"Watch out for people who have a situational value system, who can turn the charm on and off depending on the status of the person they are interacting with," Swanson writes. "Be especially wary of those who are rude to people perceived to be in subordinate roles."

The Waiter Rule also applies to the way people treat hotel maids, mailroom clerks, bellmen and security guards. Au Bon Pain co-founder Ron Shaich, now CEO of Panera Bread, says he was interviewing a candidate for general counsel in St. Louis. She was "sweet" to Shaich but turned "amazingly rude" to someone cleaning the tables, Shaich says. She didn't get the job.

Shaich says any time candidates are being considered for executive positions at Panera Bread, he asks his assistant, Laura Parisi, how they treated her, because some applicants are "pushy, self-absorbed and rude" to her before she transfers the call to him.

Just about every CEO has a waiter story to tell. Dave Gould, CEO of Witness Systems, experienced the rule firsthand when a waitress dumped a full glass of red wine on the expensive suit of another CEO during a contract negotiation. The victim CEO put her at ease with a joke about not having had time to shower that morning. A few days later, when there was an apparent impasse during negotiations, Gould trusted that CEO to have the character to work out any differences.

CEOs who blow up at waiters have an ego out of control, Gould says. "They're saying, 'I'm better. I'm smarter.' Those people tend not to be collaborative."

"To some people, speaking in a condescending manner makes them feel important, which to me is a total turnoff," says Seymour Holtzman, chairman of Casual Male Retail Group, which operates big-and-tall men's clothing stores including Casual Male XL.

How people were raised

Such behavior is an accurate predictor of character because it isn't easily learned or unlearned but rather speaks to how people were raised, says Siki Giunta, CEO of U.S. technology company Managed Objects, a native of Rome who once worked as a London bartender.

More recently, she had a boss who would not speak directly to the waiter but would tell his assistant what he wanted to eat, and the assistant would tell the waiter in a comical three-way display of pomposity. What did Giunta learn about his character? "That he was demanding and could not function well without a lot of hand-holding from his support system," she said.

It's somewhat telling, Giunta says, that the more elegant the restaurant, the more distant and invisible the wait staff is. As if the more important the customer, the less the wait staff matters. People view waiters as their temporary personal employees. Therefore, how executives treat waiters probably demonstrates how they treat their actual employees, says Sara Lee CEO Brenda Barnes, a former waitress and postal clerk, who says she is a demanding boss but never shouts at or demeans an employee.

"Sitting in the chair of CEO makes me no better of a person than the forklift operator in our plant," she says. "If you treat the waiter, or a subordinate, like garbage, guess what? Are they going to give it their all? I don't think so."

CEOs aren't the only ones who have discovered the Waiter Rule. A November survey of 2,500 by It's Just Lunch, a dating service for professionals, found that being rude to waiters ranks No. 1 as the worst in dining etiquette, at 52%, way ahead of blowing your nose at the table, at 35%.

Waiters say that early in a relationship, women will pull them aside to see how much their dates tipped, to get a read on their frugality and other tendencies. They are increasingly discussing boorish behavior by important customers at www.waiterrant.net and other blogs. They don't seem to mind the demanding customer, such as those who want meals prepared differently because of high blood pressure. But they have contempt for the arrogant customer.

Rule works with celebrities, too

The Waiter Rule also applies to celebrities, says Jimmy Rosemond, CEO of agency Czar Entertainment, who has brokered deals for Mike Tyson, Mario Winans and Guerilla Black. Rosemond declines to name names, but he remembers one dinner episode in Houston a few years back with a rude divisional president of a major music company.

When dinner was over, Rosemond felt compelled to apologize to the waiter on the way out. "I said, 'Please forgive my friend for acting like that.' It's embarrassing. They go into rages for simple mistakes like forgetting an order."

Rosemond says that particular music executive also treated his assistants and interns poorly and was eventually fired.

Odland says he saw all types of people 30 years ago as a busboy. "People treated me wonderfully and others treated me like dirt. There were a lot of ugly people. I didn't have the money or the CEO title at the time, but I had the same intelligence and raw ability as I have today.

"Why would people treat me differently? Your value system and ethics need to be constant at all times regardless of who you are dealing with."

Holtzman grew up in the coal-mining town of Wilkes-Barre, Pa., and in the 1950s saw opportunity as a waiter 90 miles away in the Catskill Mountains, where customers did not tip until the end of the week. When they tipped poorly, he would say: "Sir, will you and your wife be tipping separately?"

"I saw a lot of character, or the lack thereof," says Holtzman, who says he can still carry three dishes in his right hand and two in his left.

"But for some twist of fate in life, they're the waiter and you're the one being waited on," Barnes says.